\documentclass[binding=0.6cm, oneside]{sapthesis}%remove "english" for a thesis written in Italian
%Bachelor's (laurea triennale) thesis : Lau
\usepackage[english]{babel} %use this package for a thesis written in Italian
\usepackage[utf8]{inputenx}
\usepackage{indentfirst}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{float}
\usepackage{titlesec}
\usepackage{lettrine}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{adjustbox}
\usepackage[toc,page]{appendix}
\usepackage{listliketab}
\usepackage{csquotes}
\usepackage{tabularx}% Loads the array package
%\linespread{0.9}
\usepackage[nottoc, notlof, notlot]{tocbibind}
%\onehalfspacing
%\counterwithout{footnote}{chapter}
\usepackage{hyperref}
\hypersetup{		
			colorlinks=true,
			linkcolor=red,
                        linktoc=page,
			anchorcolor=black,
			citecolor=red,
			urlcolor=blue,
			pdftitle={The Bugs We Left Behind: Evaluating Autonomous Fuzzing Infrastructures for Overlooked Bugs and Vulnerabilities},
			pdfauthor={Matteo Sabatini},
			pdfkeywords={thesis, sapienza, roma, university}
}

%Defining macros for comments
\usepackage{xcolor}
\usepackage{xspace}
\newcommand{\mytext}[2]{\textcolor{#1}{#2}}

\newcommand{\tofix}[1]{\mytext{red}{#1}}

\newcommand{\mynote}[2]{\xspace\fbox{\bfseries\sffamily\scriptsize{#1}}
	{\small$\blacktriangleright$\textsf{\scriptsize\emph{#2}}$\blacktriangleleft$}}
\newcommand{\matteo}[1]{\mytext{magenta}{\mynote{MM}{#1}}}
\newcommand{\ziosaba}[1]{\mytext{cyan}{\mynote{ZS}{#1}}}


\title{The Bugs We Left Behind: Evaluating Autonomous Fuzzing Infrastructures for Overlooked Bugs and Vulnerabilities}
\author{Matteo Sabatini}
\IDnumber{1794627}
\course{Cybersecurity}
\courseorganizer{Facolt\`a di Ingegneria dell'informazione, informatica e statistica}
\submitdate{2023/2024}
\copyyear{2024}
\advisor{Prof. Daniele Cono D'Elia}
\coadvisor{Dott. Matteo Marini}
\authoremail{sabatini.1794627@studenti.uniroma1.it}
%Commenting this will print "Thesis not yet defended", which is good for submitting it. Then you may print it once you know the date and who the professors are
%\examdate{25/01/2025}
%\examiner{Prof. Whatever}
%\examiner{Prof. Daniele Cono D'Elia}
%\examiner{Prof. ??}

%we refer to http://ctan.mirrorcatalogs.com/macros/latex/contrib/sapthesis/sapthesis-doc.pdf for an exhaustive description of the sapthesis documentclass.




\begin{document}


%\setlength{\parindent}{0pt}    %elimina l'indentazione leggermente a destra per ogni nuovo capitolo/paragrafo
\frontmatter
\maketitle

\begin{acknowledgments}
I would like to express my gratitude to my thesis advisor, Prof. Daniele Cono D'Elia, for giving me the opportunity to deepen my knowledge in one of my favorite and also most important aspects of cybersecurity. His guidance, support and encouragement have been fundamental in the creation of this work.
\newline
I also profoundly thank my thesis co-advisor, Dr. Matteo Marini, for his expertise, suggestions and patience throughout the development of this thesis.
\end{acknowledgments}


\begin{abstract}

	\matteo{First draft}

	In a world that relies on digital systems, the security of software applications is a crucial property to protect both people and their assets. To this end, many techniques have been proposed that can detect a wide range of vulnerabilities before they can be exploited by malicious entities. The most prominent example of such techniques is \textit{Fuzz Testing}; it works by executing the software many times, generating new inputs each time to exercise as many functionalities of the code as possible. The key idea behind it is that, by producing many inputs, the \textit{fuzzer} will eventually produce one that is able to trigger a bug.

	Thanks to their \textit{fuzzing strategies}, fuzzers shine in producing inputs that allow them to execute new code as testing time passes. While reaching constantly increasing \textit{coverage}, fuzzers may miss bugs that do not cause observable behaviors at a high level. To tackle this issue, fuzzing is often used in combination with software sanitizations, a technique that detects specific silent bugs at run-time. The combination of the two techniques has become the most popular approach to detecting bugs in software.
   
	To ease the deployment of fuzzing, fuzzing frameworks are being proposed. These frameworks are fully autonomous and allow for \textit{continuous testing}. While they usually rely on a private disclosure mechanism for new bugs, these frameworks publicly release lots of data that can be analyzed. With all this accessible data, no bug should be overlooked, or an attacker could leverage the available data to detect it with a much lower effort than running fuzzing campaigns, and potentially exploit it to attack the target software.
	   
	In this thesis, we are going to evaluate fuzzing frameworks for possibly overlooked bugs. We will be exploring two main directions: first, we are going to evaluate fully autonomous mechanisms, where suboptimal configurations or procedures can cause some bugs to be missed; then, we are going to evaluate another class of frameworks where the human factor is crucial in the detection of new bugs and vulnerabilities.
	We will show that, unfortunately, these frameworks are indeed missing a relevant amount of bugs. These bugs can be detected starting from publicly available data with low effort and many of them have security implications. After reporting all the bugs we found during our evaluation, we contacted the maintainers of such frameworks and proposed new approaches to limit the amount of overlooked bugs.


\ziosaba{Q1: Which are the two frameworks mentioned? I'm not sure that I'm following which are the two directions, assuming you're referring to OSS-Fuzz and FuzzBench}

\ziosaba{Q2: "We contacted the maintainers of such framework" is something that I have yet to do, or am I missing something? We contacted the developers of the project, not the maintainers at Google}

\end{abstract}




\tableofcontents


\titleformat{\chapter}[display]  
{\normalfont\Huge\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\huge}  
\titlespacing{\chapter}{0pt}{0pt}{0pt}  

\mainmatter




\input{chapters/1-introductions.tex}

\input{chapters/2-background.tex}

\input{chapters/3-methodology.tex}

\input{chapters/4-results.tex}

\input{chapters/5-conclusions.tex}



\backmatter
\phantomsection
\bibliographystyle{sapthesis} % BibTeX style
\bibliography{bibliography}




\end{document}