\chapter{Results}
\chapter{Results}
\ \\
To correctly analyze and categorize the bugs discovered I had to perform \textit{bug deduplication}, a technique used to remove all inputs that produced the same results, which is crucial to remove any unnecessary data from the results and make the bug analysis work less tedious for the developer.
\newline \newline
There are several approaches and strategies that can be applied to deduplicate bugs, and it's important to mention that there is no fool-proof methodology that perfect results on all possible scenarios.
\newline
Given that this work focused on OSS-Fuzz, I decided to employ the same approach used by them when generating bug reports, where they use the fields "Crash Type" and "Crash state" as the main references (Figure \ref{fig:issue}).
\newline
In conclusion, each bug will be defined by its error type and the last 3 stack entries from where the error occurred.
 
\ \\ \newline \newline
Briefly explain the python scripts used to retrieve the results...



\ \\
\matteo{Brief introduction to this chapter}

\section{OSS-Fuzz}

\matteo{Put here all the data, make a table with aggregated results.}

\matteo{Say something about the presence of sanitizers and how many bugs we found when that sanitizer was present vs when it was not present}

\matteo{Say something about why those bugs have been overlooked. I think we have a past mail on this; our hypothesis is that, when a sanitizer was not enabled, then trivially the fuzzer could not detect certain bugs. When that sanitizer was enabled maybe certain campaigns with one sanitizer generated a testcase that triggered a bug with another sanitizer and was also saved in the queue (e.g. it produced new coverage).}

\matteo{Highlight the crashes we found in gpac and in vlc; also say that we found gpac ones while they were still in private disclosure}

\matteo{Do one or two case studies (in subsetions); I would talk about gpac, we have something to say about all the MSan bugs we found and the interaction with the CEO. The developer also wrote in their report on github that MSan bugs were giving them non-deterministic behaviors in their software. Then maybe vlc? It has 2 sanitizer and yet we found bugs for all sanitizers plus two crashes.}

\matteo{Make a new subsection and talk about what can we learn about this, and how can this issue be fixed by Google.}

\section{FuzzBench}

\matteo{Kind of the same we did for OSS-Fuzz, let's wait for some data before drafting something, I guess.}

\matteo{We can distinguish between "regular" fuzzbench and sbft? Let's see what the numbres say.}

\section{Discussion}
Discuss the overall results, what was expected and what was unexpected...
\newline \newline
Discuss the importance of such results, what can be inferred...
\newline \newline
??? Discuss about the reports  where???
